Maintenance planning on French military aircraft operations

### 2018-06-25 R/presentations/MOSIM_presentation/presentation.Rmd
MOSIM presentation added

---
title: "Maintenance planning on French military aircraft operations"
author: |
    | Franco Peschiera, Alain Haït, Olga Battaïa, Nicolas Dupin
    | \tiny (franco.peschiera@isae-supaero.fr)
institute: "ISAE SUPAERO"
date: "February 22, 2018"
output: 
  beamer_presentation:
    theme: "Berlin"
    toc: true
    slide_level: 2
    incremental: yes
    fig_height: 4
    # footer: "ISAE-SUPAERO, Université de Toulouse, France"
    includes:
        in_header: header.tex
  slidy_presentation:
    css: ./../../css/baobab_MH.css
    incremental: yes
    footer: "ISAE-SUPAERO, Université de Toulouse, France"
    slide_level: 2
    toc: true
nocite: '@*'
bibliography: MFMP.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
setwd("../")
source('functions/params.R')
source('functions/import_results.R')
exp_directory = PATHS[['experiments']] %>% paste0('201802141539/')
gantt <- print_solution(exp_directory, max_resources = 30)
show_gantt <- knitr::opts_knit$get("rmarkdown.pandoc.to")=="slidy"
```

@@

if (show_gantt){
    htmltools::HTML('<div style="font-size: 20px;width:100%">')
    gantt
    htmltools::HTML("</div>")
} else {
    knitr::include_graphics('./../../img/calendar.png')
}

@@

\pause
```{r out.width="150pt", echo=FALSE}
knitr::include_graphics("./../../img/progress.png.png")
```

@@

Comparison of two objectives: max availability or maintenance capacity.
Different weights were used for the two objectives: $W_1, W_2 \in [0..1]$ with pace of 0.1.
\pause
```{r out.width="180pt", echo=FALSE}
knitr::include_graphics("./../../img/multiobjective.png")
```

>>>>

---
title: "Maintenance planning on French military aircraft operations"
author: |
    | Franco Peschiera, Alain Haït, Olga Battaïa, Nicolas Dupin
institute: "ISAE SUPAERO"
date: "June 27, 2018"
output: 
  beamer_presentation:
    theme: "Berlin"
    toc: true
    slide_level: 2
    incremental: yes
    fig_height: 4
    # footer: "ISAE-SUPAERO, Université de Toulouse, France"
    includes:
        in_header: header.tex
  slidy_presentation:
    css: ./../../css/baobab_MH.css
    incremental: yes
    footer: "ISAE-SUPAERO, Université de Toulouse, France"
    slide_level: 2
    toc: true
nocite: '@*'
bibliography: MFMP.bib
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
path_to_R_dir <- "./../../"
setwd(path_to_R_dir)
source('functions/params.R')
source('functions/import_results.R')
exp_directory = PATHS[['experiments']] %>% paste0('201802141539/')
gantt <- print_solution(exp_directory, max_resources = 30)
show_gantt <- knitr::opts_knit$get("rmarkdown.pandoc.to")=="slidy"
```

@@

if (show_gantt){
    htmltools::HTML('<div style="font-size: 20px;width:100%">')
    gantt
    htmltools::HTML("</div>")
} else {
    knitr::include_graphics('../img/calendar.png' %>% paste0(path_to_R_dir, .))
}

@@

\pause
```{r out.width="150pt", echo=FALSE}
knitr::include_graphics("../img/progress.png.png" %>% paste0(path_to_R_dir, .))
```

@@

Comparison of two objectives: max availability or maintenance capacity.
Different weights were used for the two objectives: $W_1, W_2 \in [0..1]$ with pace of 0.1.
\pause
```{r out.width="180pt", echo=FALSE}
knitr::include_graphics("../img/multiobjective.png" %>% paste0(path_to_R_dir, .))
```
